---
title: "Deep Learning Starter Code"
format: docx
editor: visual
---

# Ready to Train a Neural Network?

Install the `nnet` package!

```{r}

```

Load libraries.

```{r}
# Load packages
library(tidyverse)
library(tidymodels)
```

# Data Wrangling

```{r}
# Import data, wrangle S1 into segment, coerce factors, and select predictors.
roomba_survey <- read_csv("roomba_survey.csv") |> 
  rename(segment = S1) |> 
  mutate(
    segment = case_when(
      segment == 1 ~ "own",
      segment == 3 ~ "shopping",
      segment == 4 ~ "considering"),
    # convert numeric categorical variables into factors for dummies
    segment = factor(segment),
    D2HomeType = factor(D2HomeType),
    D3Neighborhood = factor(D3Neighborhood),
    D4MaritalStatus = factor(D4MaritalStatus),
    D6Education = factor(D6Education)) |> 
  select(
    segment, contains("RelatedBehaviors"), contains("ShoppingAttitudes"), 
    D1Gender, D2HomeType, D3Neighborhood, D4MaritalStatus, D6Education
  )
```

# Feature Engineering

```{r}
set.seed(42)

# Split data based on segment.
roomba_split <- initial_split(roomba_survey, prop = 0.75, strata = segment)

# Feature engineering.
roomba_recipe <- training(roomba_split) |>
  recipe(
    segment ~ .
  ) |>
  # create dummy variables - using all_nominal_predictors(),
  # rather than all_nominal(), -segment
  step_dummy(all_nominal_predictors()) |> 
  # remove variables that have a single value (zero variance) - why?
  step_zv(all_predictors()) |>
  # normalize all predictors
  step_normalize(all_predictors())
```

# Fit a Multilayer Perceptron

There are *many* different types of neural networks. A common one is a **multilayer perceptron**, which has a single hidden layer.

```{r}
# Set the model, engine, and mode.
nn_model_01 <- mlp() |> 
  set_engine(engine = "nnet") |> 
  set_mode("classification")

nn_model_01
```

Create a workflow that combines the recipe and model and fit it.

```{r}
# Create a workflow.
nn_wf_01 <- workflow() |> 
  add_recipe(roomba_recipe) |> 
  add_model(nn_model_01)

# Fit the workflow.
nn_fit_01 <- fit(nn_wf_01, data = training(roomba_split))
```

# Model Evaluation

So far, we have repeated the same steps every time we want to evaluate a model.

* Generate predictions from the fitted model for the `test` data
* Join the predictions as a new column in the `test` data
* Compute the accuracy using the prediction column and the column of true values

# Functions Review

- We should try to write functions that are as *general* as possible.
- To create a `tidy` function, i.e., a function that can accept an un-quoted variable name as an argument place `{{ }}` around that variable name wherever it occurs in the function.

```{r}
fit_accuracy <- function(fit, testing_data, truth) {
  ###
  # - fit: a fitted model
  # - testing_data: test data for which predictions will be generated
  # - truth: name of the target (Y) variable contained in testing_data
  eval_results <- fit |> 
    predict(new_data = testing_data) |>
    bind_cols(testing_data) |>
    accuracy(truth = {{truth}}, estimate = .pred_class)
  
  return(eval_results)
}
```

Let's look at the accuracy on the testing data.

```{r}
# Compute model accuracy.
fit_accuracy(nn_fit_01, testing(roomba_split), segment)
```

**OOF!** That accuracy isn't great.

# Hyperparameter Tuning

There are a *lot* of [potential hyperparameters to tune](https://playground.tensorflow.org), but we'll focus on three.

- `hidden_units` the number of hidden units in the single layer
- `epochs` the number of training iterations
- `penalty` a penalty term to help fight overfitting

The `activation` function is set based on the model mode. You can experiment with `"relu"` instead of the default of `"linear"` for regression and `"softmax"` for classification.

```{r}
# Set up v-fold cross-validation based on segment.
roomba_cv <- vfold_cv(training(roomba_split), v = 10, strata = segment)

# Set the model, engine, and mode.
nn_model_02 <- mlp(hidden_units = tune(), epochs = tune(), penalty = tune()) |> 
  set_engine(engine = "nnet") |> 
  set_mode("classification")

# Update the workflow.
nn_wf_02 <- nn_wf_01 |> 
  update_model(nn_model_02)

# Tune the hyperparameters by using cross-validation.
nn_tune <- nn_wf_02 |> 
  tune_grid(resamples = roomba_cv)
```

Let's examine the accuracy for each model version displayed in descending order of accuracy.

```{r}
nn_tune |>
  collect_metrics(summarize = FALSE) |>
  filter(.metric == "accuracy") |>
  group_by(.config) |>
  summarize(avg_accuracy = mean(.estimate)) |>
  arrange(desc(avg_accuracy))
```

Select the best model and finalize our workflow.

```{r}
# Select the best fitting model.
nn_tune_best <- nn_tune |> 
  select_best(metric = "accuracy")

# Finalize the workflow.
nn_wf_final <- nn_wf_02 |> 
  finalize_workflow(nn_tune_best)

nn_wf_final
```

Now let's fit the finalized workflow on the entire training data.

```{r}
# Fit the tuned workflow to the whole training data set
nn_fit_02 <- fit(nn_wf_final, data = training(roomba_split))

# Compute model accuracy.
fit_accuracy(nn_fit_02, testing(roomba_split), segment)
```

## Live Coding

Let's compare our most complicated model (neural network) to our simplest model (logistic regression) to predict response to the most recent marketing campaign in the iFood data.

```{r}
# Load packages.

# Set the seed.

# Import data and wrangle our dependent variable

# Split data

# Create v-fold cross-validation

# create recipe (Feature engineering)
```

Logistic regression modeling.

```{r}
# create model

# create workflow

# fit workflow to CV folds

# compute accuracy
```

Neural network modeling.

```{r}
# repeat the above for the neural network, with tuning
```

Which model did better? Use the best model on the test data.
