---
title: "Exercise 16"
author: "Cameron Bale"
format: docx
---

Return to the set of models from the previous two exercises.

1. Set up workflows for a decision tree, a random forest, and a neural network. Be sure you're making a fair comparison by fitting the previous models (hyperparameter tuning included, where applicable), on the same random training and testing split using the same recipe (i.e., you should create dummies, remove constant features, and standardize features for all models.
2. Train and tune each model (except the logistic regression since it doesn't have hyperparameters) using cross-validation on the training data.
3. Create a data frame comparing the performance of all three models on the test data. Which is the best-fitting model so far? Use confusion matrices to explore how the best-fitting model is doing better than the competing models. Interpret what you find. For example, is one of the models notably better at predicting one or more of the segments of interest?
4. Render the Quarto document into Word and upload to Canvas.

**Five points total, one point each for:**

- **Doing an initial random split of the data.**
- **Fitting a logistic regression, tuned decision tree, and tuned random forest using the same data and recipe.**
- **Fitting a tuned multilayer perceptron on the same data.**
- **Creating a data frame to compare all of the models on the same testing data along with confusion matrices to help interpret why the best-fitting model is best.**
- **Submitting a rendered Word document.**

## Data Prep and Feature Engineering

We are again encoding `segment` as two categories and using the same predictors as before.

```{r}
# Load packages.
library(tidyverse)
library(tidymodels)

# Set the seed.
set.seed(42)

# Import data and wrangle S1 into segment.
roomba_survey <- read_csv("roomba_survey.csv") |> 
  rename(segment = S1) |> 
  mutate(
    segment = case_when(
      segment == 1 ~ "own or shopping",
      segment == 3 ~ "own or shopping",
      segment == 4 ~ "considering"
    ),
    segment = factor(segment)
  )

# Split data based on segment.
roomba_split <- initial_split(roomba_survey, prop = 0.75, strata = segment)

# Use v-fold cross-validation based on segment.
roomba_cv <- vfold_cv(training(roomba_split), v = 10, strata = segment)

# Feature engineering.
roomba_recipe <- training(roomba_split) |>
  recipe(
    segment ~ CleaningAttitudes_1 + CleaningAttitudes_2 + CleaningAttitudes_3 + 
      CleaningAttitudes_4 + CleaningAttitudes_5 + CleaningAttitudes_6 + 
      CleaningAttitudes_7 + CleaningAttitudes_8 + CleaningAttitudes_9 + 
      CleaningAttitudes_10 + CleaningAttitudes_11 +
      D1Gender + D2HomeType + D3Neighborhood + D4MaritalStatus
  ) |>
  step_dummy(all_nominal_predictors()) |> 
  step_normalize(all_predictors())
```

## Fit Models

Let's fit all of the competing models on the same training data.

```{r}
# Logistic regression.
roomba_lr <- logistic_reg() |> 
  set_engine(engine = "glm")

roomba_wf_lr <- workflow() |> 
  add_recipe(roomba_recipe) |> 
  add_model(roomba_lr)

fit_lr <- fit(roomba_wf_lr, data = training(roomba_split))

# Decision tree.
roomba_dt <- decision_tree(tree_depth = tune(), min_n = tune()) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

roomba_wf_dt <- roomba_wf_lr |> 
  update_model(roomba_dt)

tune_dt <- tune_grid(roomba_wf_dt, resamples = roomba_cv)

tune_dt_best <- tune_dt |> 
  select_best(metric = "accuracy")

roomba_wf_dt <- roomba_wf_dt |> 
  finalize_workflow(tune_dt_best)

fit_dt <- fit(roomba_wf_dt, data = training(roomba_split))

# Random forest.
roomba_rf <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) |> 
  set_engine(engine = "randomForest") |> 
  set_mode("classification")

roomba_wf_rf <- roomba_wf_lr |> 
  update_model(roomba_rf)

tune_rf <- tune_grid(roomba_wf_rf, resamples = roomba_cv)

tune_rf_best <- tune_rf |> 
  select_best(metric = "accuracy")

roomba_wf_rf <- roomba_wf_rf |> 
  finalize_workflow(tune_rf_best)

fit_rf <- fit(roomba_wf_rf, data = training(roomba_split))

# Neural network.
roomba_nn <- mlp(hidden_units = tune(), epochs = tune(), penalty = tune()) |> 
  set_engine(engine = "nnet") |> 
  set_mode("classification")

roomba_wf_nn <- roomba_wf_lr |> 
  update_model(roomba_nn)

tune_nn <- tune_grid(roomba_wf_nn, resamples = roomba_cv)

tune_nn_best <- tune_nn |> 
  select_best(metric = "accuracy")

roomba_wf_nn <- roomba_wf_nn |> 
  finalize_workflow(tune_nn_best)

fit_nn <- fit(roomba_wf_nn, data = training(roomba_split))
```

## Compare Predictive Fit

Let's create a data frame and compare predictive fit using a function.

```{r}
# Fit accuracy function.
fit_accuracy <- function(fit, testing_data, truth) {
  fit |> 
    predict(new_data = testing_data) |>
    bind_cols(testing_data) |>
    accuracy(truth = {{truth}}, estimate = .pred_class)
}

# Create a table of predictive fit.
bind_cols(
  model = c("lr", "dt", "rf", "nn"),
  bind_rows(
    fit_accuracy(fit = fit_lr, testing_data = testing(roomba_split), truth = segment),
    fit_accuracy(fit = fit_dt, testing_data = testing(roomba_split), truth = segment),
    fit_accuracy(fit = fit_rf, testing_data = testing(roomba_split), truth = segment),
    fit_accuracy(fit = fit_nn, testing_data = testing(roomba_split), truth = segment)
  )
)
```

The neural network performs best with a predictive accuracy of `0.702`. The next-best is a two-way tie between logisitc regression and the decision tree.

Let's use confusion matrices to explore why the neural network is doing better.

```{r}
# Confusion matrix function.
conf_matrix <- function(fit, testing_data, truth) {
  fit |> 
    predict(new_data = testing_data) |>
    bind_cols(testing_data) |>
    conf_mat(truth = {{truth}}, estimate = .pred_class)
}

conf_matrix(fit = fit_lr, testing_data = testing(roomba_split), truth = segment)
conf_matrix(fit = fit_dt, testing_data = testing(roomba_split), truth = segment)
conf_matrix(fit = fit_nn, testing_data = testing(roomba_split), truth = segment)
```

The final predictions from these three models are incredibly similar. The decision tree is predicting everyone as considering. The logistic regression correctly predicts one person as own or shopping, but also gets a false positive, which is why the accuracy is the same as the decision tree. The neural network is able to correctly predict one person as own or shopping without a false positive prediction as well, which is why it edges out these other models on accuracy.

Ultimately, we should go back and make our model selection based on the cross-validation results, not a single test data set.
