---
title: "Neural Network vs. Logistic Regression"
format: docx
editor: visual
---

Let's compare our most complicated model (neural network) to our simplest model (logistic regression) to predict response to the most recent marketing campaign in the iFood data.

```{r}
# Load packages.

# Set the seed.
set.seed(916)

# Import data and wrangle our dependent variable
ifood <- read_csv("ifood.csv")
```

Let's do some data cleaning.

Let's first drop observations with missing values.

```{r}
ifood <- ifood |>
  drop_na()
```

Next, let's handle 'nonsense' values for marital status.

```{r}
ifood |>
  distinct(Marital_Status)

drop_marital <- c("Alone", "Absurd", "YOLO")

ifood <- ifood |>
  filter(!Marital_Status %in% drop_marital) |>
  select(-Dt_Customer)
```

Let's construct segments based on the number of responses to past marketing campaigns.

```{r}
ifood <- ifood |>
  mutate(total_responses = AcceptedCmp3 +
           AcceptedCmp1 +
           AcceptedCmp2 +
           AcceptedCmp4 +
           AcceptedCmp5 +
           Response)
```

Construct a histogram showing the number of responses for consumers.

```{r}
ifood |>
  ggplot(aes(x = total_responses)) +
  geom_histogram()
```

Let's define our target variable `segment` based on the number of past campaign responses.

```{r}
ifood <- ifood |>
  mutate(segment = case_when(
    total_responses == 0 ~ "Non-responsive",
    total_responses == 1 ~ "Somewhat responsive",
    total_responses %in% c(2, 3, 4, 5) ~ "Highly Responsive"),
    segment = factor(segment))
```

## Pre-processing Steps

```{r}
# Split data
ifood_split <- initial_split(ifood, prop = 0.80, strata = segment)

# Create v-fold cross-validation
cv_split <- vfold_cv(training(ifood_split), v = 8, strata = segment)

# create recipe (Feature engineering)
ifood_recipe <- training(ifood_split) |>
  recipe(segment ~ .) |>
  # create dummy variables - using all_nominal_predictors(),
  # rather than all_nominal(), -segment
  step_dummy(all_nominal_predictors()) |> 
  # remove variables that have a single value (zero variance) - why?
  step_zv(all_predictors()) |>
  # normalize all predictors
  step_normalize(all_predictors())
```

Logistic regression modeling.

```{r}
# create model
lr_model <- logistic_reg() |>
  set_engine("glm")

# create workflow
lr_workflow <- workflow() |>
  add_recipe(ifood_recipe) |>
  add_model(lr_model)

# fit workflow to CV folds
lr_cv_results <- lr_workflow |>
  fit_resamples(cv_split)

# compute accuracy
```

Neural network modeling.
